Self-sustained carbon monoxide oxidation oscillations on size-selected platinum nanoparticles at atmospheric pressure

### 2012-10-18 paper.tex
Added a missing figure, updated a few wrong numbers

\footnotetext{\textit{$^{a}$~CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark. Fax: XX XXXX XXXX; Tel: XX XXXX XXXX; E-mail: ibchork@fysik.dtu.dk}}
\footnotetext{\textit{$^{b}$~CINF, Department of Micro- and Nanotechnology, Technical University of Denmark, Ørsteds Plads, B 345B, 2800 Lyngby, Denmark. Fax: XX XXXX XXXX; Tel: XX XXXX XXXX; E-mail: ibchork@fysik.dtu.dk}}
%\footnotetext{\textit{$^{b}$~CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark}}

@@

In this study Pt nanoparticles were investigated which, compared to a single crystal or a thin film, is a very rough surface. It is to be expected that the particles will initially favor the reduced state. As the reaction runs the gas composition towards the outlet of the reactor will become more oxidizing increasing the oxidation rate of the particles (illustrated in Figure~\ref{fgr:full_oscillation}). Gradually, as the particles toward the outlet oxidizes the turn-over will increase and the general CO concentration will decrease promoting more and more particles to oxidize which will gradually be seen in the QMS as an increase in CO$_2$ and a decrease in CO. As the CO concentration decreases the light-off temperature will decrease hence approaching the constant temperature of the sample resulting in a steep increase in reactivity. It is important to note that the fraction of oxidized particles needed to achieve full conversion is not known. We are currently investigating new methods for gaining insight into the nature of the nanoparticles in the reactor but the low coverage and the design of the reactor makes this a challenging task. If not all particles are oxidized at light-off they will now oxidize much faster due to the low CO-concentration. The further increased rate will not be visible in the QMS since the reactor is already in full conversion. As most of the particles are now oxidized they will become more and more roughened and gradually return to the reduced state. Fewer and fewer oxidized particles will be responsible for the activity increasing the roughing rate of the remaining active particles. Just before the overall activity drops only a fraction of the particles participates in the reaction and the deactivation will happen very suddenly. Once these potentially few particles eventually becomes sufficiently rough they will reduce and lose activity hence completing the oscillation cycle. It should be noted that our group has recently measured turnover frequencies of CO oxidation on Pt in excess of $10^{6}$s$^{-1}$ per site corresponding to as little as $\sim$300 Pt nanoparticles contributing to the reactivity just before the end of the high-activity cycle.

@@

%\subsection{This is the subsection heading style}
%Section headings can be typeset with and without numbers.\cite{Gong2004} \cite{Hendriksen2010}

%\subsubsection{This is the subsubsection style.~~} These headings should end in a full point.

%\paragraph{This is the next level heading.~~} For this level please use \texttt{\textbackslash paragraph}. These headings should also end in a full point.

%\section{Equations}

%Equations can be typeset inline \textit{e.g.} $ y = mx + c$ or displayed with and without numbers:

% \[ A = \pi r^2 \]

%\begin{equation}
%  \frac{\mathrm{\gamma}}{\mathrm{\epsilon}x} r^2 = 2r
%\end{equation}

%\section{Graphics and tables}
%\subsection{Graphics}
%Graphics should be inserted on the page where they are first mentioned (unless they are equations, which appear in the flow of the text).

%\subsection{Tables}
%Tables typeset in RSC house style do not include vertical lines. Table footnote symbols are lower-case italic letters and are typeset at the bottom of the table. Table captions do not end in a full point.

%\begin{table}[h]
%\small
%  \caption{\ An example of a caption to accompany a table}
%  \label{tbl:example}
%  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}lll}
%    \hline
%    Header one/units & Header two & Header three \\
%    \hline
%    1 & 2 & 3 \\
%    4 & 5 & 6 \\
%    7 & 8 & 9 \\
%    10 & 11 & 12 \\
%    \hline
%  \end{tabular*}
%\end{table}

%Adding notes to tables can be complicated.  Perhaps the easiest
%method is to generate these manually.

% an example of a two-column table
%\begin{table*}
%\small
  %\caption{\ An example of a caption to accompany a table, table captions do not end in a full point}
  %\label{tbl:example}
  %\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lllllll}
    %\hline
    %Header one & Header two & Header three & Header four & Header five & Header six  & Header seven\\
    %\hline
    %1 & 2 & 3 & 4 & 5 & 6  & 7\\
    %8 & 9 & 10 & 11 & 12 & 13 & 14 \\
    %15 & 16 & 17 & 18 & 19 & 20 & 21\\
    %\hline
  %\end{tabular*}
%\end{table*}

%You can also put lists into the text. You can have bulleted or numbered lists of almost any kind. 
%The \texttt{mhchem} package can also be used so
%that formulae are easy to input: \texttt{\textbackslash ce\{H2SO4\}} gives \ce{H2SO4}.

%\section{Conclusions}
%The conclusions section should come at the end of article. For the reference section, the style file rsc.bst can be used to generate the correct reference style.\footnote[4]{Footnotes should appear here. These might include comments relevant to but not central to the matter under discussion, limited experimental and spectral data, and crystallographic data.}
 %For footnotes in the main text of the article please number the footnotes to avoid duplicate symbols. e.g.  \footnote[num]{your text} the corresponding author \ast counts as footnote 1, ESI as footnote 2, e.g. if there is no ESI, please start at [num]=[2], if ESI is cited in the title please start at [num]=[3] etc. Please also cite the ESI within the main body of the text using \dag.

%The \balance command can be used to balance the columns on the final page if desired. It should be placed anywhere within the first column of the last page.

%\balance

%If notes are included in your references you can change the title from 'References' to 'Notes and references' using the following command:
%\renewcommand\refname{Notes and references}

>>>>

\footnotetext{\textit{$^{a}$~CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark. E-mail: ibchork@fysik.dtu.dk}}
\footnotetext{\textit{$^{b}$~CINF, Department of Micro- and Nanotechnology, Technical University of Denmark, Ørsteds Plads, B 345B, 2800 Lyngby, Denmark.}}
%\footnotetext{\textit{$^{b}$~CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark}}

@@

In this study Pt nanoparticles were investigated which, compared to a single crystal or a thin film, is a very rough surface. It is to be expected that the particles will initially favor the reduced state. As the reaction runs the gas composition towards the outlet of the reactor will become more oxidizing increasing the oxidation rate of the particles (illustrated in Figure~\ref{fgr:full_oscillation}). Gradually, as the particles toward the outlet oxidizes the turn-over will increase and the general CO concentration will decrease promoting more and more particles to oxidize which will gradually be seen in the QMS as an increase in CO$_2$ and a decrease in CO. As the CO concentration decreases the light-off temperature will decrease hence approaching the constant temperature of the sample resulting in a steep increase in reactivity. It is important to note that the fraction of oxidized particles needed to achieve full conversion is not known. We are currently investigating new methods for gaining insight into the nature of the nanoparticles in the reactor but the low coverage and the design of the reactor makes this a challenging task. If not all particles are oxidized at light-off they will now oxidize much faster due to the low CO-concentration. The further increased rate will not be visible in the QMS since the reactor is already in full conversion. As most of the particles are now oxidized they will become more and more roughened and gradually return to the reduced state. Fewer and fewer oxidized particles will be responsible for the activity increasing the roughing rate of the remaining active particles. Just before the overall activity drops only a fraction of the particles participates in the reaction and the deactivation will happen very suddenly. Once these potentially few particles eventually becomes sufficiently rough they will reduce and lose activity hence completing the oscillation cycle. It should be noted that our group has recently measured turnover frequencies of CO oxidation on Pt of almost $10^{5}$s$^{-1}$ per site corresponding to as little as $\sim$50000 Pt nanoparticles contributing to the reactivity just before the end of the high-activity cycle. This corresponds to an area of $\sim$0.5 ppm of the reactor area suggesting that in situ studies become challenging as such a minority of the reactor volume could account for all the reactivity. Attempts to see any thermal signal from such small areas has so far been in vain.

@@
